---
title: "W_UP_01"
author: "Louie"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
ggplot(mydata, aes(x = position, y = pushups)) +
  geom_boxplot() +
  labs(title = "Box Plot of Pushups by Position",
       x = "Position",
       y = "Pushups")
```
  
The box with Line is lower than The Box with skill. The individuals with skill are doing far more pushups the than the ones with line, about %15 more.
  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
  
Q3 is lower than Q1 meanwhile skill Q1 and Q3 is greater than line.Skill has a far more larger number than line does. line has a median of 14.5 while a skill has a median of 47.5. almost 3x the amount.
   
 
## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```
As the data shows the players with skill can do far more pushups than the players with Line.
  


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
In conclusion, the box plot displayed above and the Sample test conclude that the players with Sill can do almost 3x the amount of push ups than the players with line. Taking the results of pushups, positions and my data helped conclude this fact. using chat gpt to acquire the appropriate code helped with this conclusion. chat GPT helped alot with command codes.  
  